---
title: "Grossepieper_Nils_Assignment01_R"
author: "Nils Grossepieper"
date: "2023-03-26"
output: html_document
---

### __Assignment I: Importing, cleaning and merging__
\

##### __0. Preparations:__

In the first step I have to load all the important packages for this assignment.
All necessary packages have already been downloaded on my PC.\
In the next step I set up the working directory.\
In the third step I import the data files and name them according to the set up 
descriptions.\

```{r, warning=FALSE, message=FALSE}
# 1. load the important packages
library(tidyverse)
library(readxl)

# 2. set up the working directory
setwd("C:/Users/gross/OneDrive/Dokumente/Grossepieper_Nils_Assignment01")

# 3. import the data files
financials_annual <- read_excel("data/financials_annual.xlsx", na = c("", "NA"), sheet = 1)
company_codes <- read_excel("data/financials_annual.xlsx", na = c("", "NA"), sheet = 2)
item_codes <- read_excel("data/financials_annual.xlsx", na = c("", "NA"), sheet = 3)
```
\


##### __1. Exercise:__

Read the article Tidy Data (Wickham, 20171). According to Wickham’s definition of “tidy data”, describe
what is problematic about the data set financials_annual and why.
\

##### __Answer:__

The data set "financials_annual" has the following problems which contradicts
with the concept of tidy data: \

1.) I do not have the case that every variable is placed in its own column,
sine I have twenty columns for the same variable. \

2.) I also do not have the case that every observation is placed in its own
row, since I have observations for twenty separate years in one row. \

3.) At least the condition that every value is placed in its own cell is 
fulfilled. \

At the end I can say that the data set financials_annual does only fulfill 
one of the tidy data conditions, which means that this data set is not in the
tidy data format. \
\


##### __2. Exercise:__

Make the transformations needed so that the data can be described as “tidy” \

```{r}
# Have a look at the three data sets:
head(financials_annual, 10)
company_codes
item_codes
```

```{r, results='hide', warning=FALSE}
# Take a look at the data set:
glimpse(financials_annual)

# Transform every column to a column with characters:
string_vec <- c("2013", "2014", "2018", "2019")
financials_annual <- financials_annual %>% mutate(across(string_vec, as.character))

# Check whether the transformation was successful:
glimpse(financials_annual)

# Now I need to transform the data in the long format:
financials_annual_tidy <- financials_annual %>%
  pivot_longer(cols = "2000":"2019", names_to = "Year", values_to = "Finance")


```
```{r}
# Have a look at the new tidy data set:
head(financials_annual_tidy, 10)
```
\


##### __3. Exercise:__

Merge the company_name (given in the data frame company_codes) to the financial data. \

```{r}
# I have to do a string split to bring the observations of the variable "Code"
# in the right format so they can merge with the other data set:
financials_annual_tidy <- financials_annual_tidy %>%
  mutate(company_code = Code %>% str_sub(, end = -10))

# In advanced I can also bring the "item_code" in the right format:
financials_annual_tidy <- financials_annual_tidy %>%
  mutate(item_code = Code %>% str_sub(start = -8, ))
financials_annual_tidy$item_code <- gsub(")", "", financials_annual_tidy$item_code)

# Merge the two data sets "financial_annual_tidy" and "company_codes":
financials_annual_merge <- left_join(financials_annual_tidy, company_codes,
                                     by = "company_code")

# Have a look at the new data set:
head(financials_annual_merge, 10)

```
\


##### __4. Exercise:__

The variable names (i.e., column names) should be given by the item descriptions item_descr (given
in the data frame item_codes), not by the item_code. \

```{r}
# Merge the two data sets "financial_annual_merge" and "item_codes":
financials_annual_final <- left_join(financials_annual_merge, item_codes,
                                     by = "item_code")

# Have a look at the new data set:
head(financials_annual_final, 10)

# Now I can delete some variables that I do  not need anymore to make my data
# set more clear:
financials_annual_final$Code <- NULL
financials_annual_final$company_code <- NULL
financials_annual_final$item_code <- NULL

# Reorder the columns in a clearer way:
financials_annual_final <- financials_annual_final %>%
  select(company_name, Year, Finance, item_descr)

# I want the item descriptions as columns so I have to transform the data set
# into the long format:
annual_finances <- financials_annual_final %>%
  pivot_wider(id_cols = c(company_name, Year), names_from = item_descr, 
              values_from = Finance)

# Have a look at the new data set:
head(annual_finances, 10)

```
\


##### __5. Exercise:__

Before you proceed, check if …\
… each variable is placed in its own column.\
… each observation is placed in its own row.\
… each value is placed in its own cell.\
… each variable has an adequate variable type.\
… missing values are correctly identified as such.\
… the the order of observations is reasonable.\

##### __Answer:__

Each variable is placed in its own column. \
Each observation is placed in its own row. \
Each value is placed in its own cell. \
Each variable is in an adequate type. \
Missing values are identified. \
The order of observations is reasonable. \
\


##### __6. Exercise:__

The .csv-file company_info.csv contains additional information on the ten companies from a different
source. Read the file into your environment as a data frame named company_info. \

```{r, warning=FALSE, message=FALSE}
# Read in the data "company info":
company_info <- read_csv2("data/company_info.csv", na = c("", "NA"), skip = 1)

```
\


##### __7. Exercise:__

Is this a tidy data set? Why (not)? \

##### __Answer:__

1. Each variable forms a column. \
This condition is fulfilled since you have five variables and each is in its 
own column. \
2. Each observation forms a row. \
This condition is also fulfilled, since we have ten companies (observations)
and each of them has its own row. \
3. Each type of observational unit forms a table. \
Also the last condition is fulfilled. \
\


##### __8. Exercise:__

Compare the company names given in company_info with the ones you have in the tidy financial data.
What do you notice? \

```{r}
# Take a look at the two data sets:
head(company_info, 10)
head(annual_finances, 10)

# The company names in our original data sets are all capital letters, while in 
# the data set "company_info"  the company names are written with small letters

```
\


##### __9. Exercise:__

Make the changes to company_info$company_name that are needed so that the company names can
serve as keys. \

```{r}
# Make the letters of the company names capital:
company_info$company_name <- toupper(company_info$company_name)

# Take a look at the new format:
head(company_info, 10)

```
\


##### __10. Exercise:__

Join the two data sets such that all observations in the financial data are kept and the additional
information from company_info is appended \

```{r}
# Now I join the two data sets:
final_data_set <- left_join(annual_finances, company_info, by = "company_name")

```
\


##### __11. Exercise:__

Print the first ten and the last ten observations of the joined data set. \

```{r}
# The first ten observations:
head(final_data_set, 10)

# The last ten observations:
tail(final_data_set, 10)

```
